From Reversible Programs to \\ Univalent Universes and Back

### 2021-07-01 Pi+/paper/finite.tex
Fix latex

Connecting it all back to the language $\PiLang$ we are dealing with, it is possible to construct a simlar, yet simplified language $\PiLangHat$ (introduced at \cref{sec:equivalence}), which operates on adjacent transpositions, but still preservers much of $\PiLang$ structure. Thus, for the proof, a presentation based on adjacent transpositions is used, called \emph{Coxeter presentation}. Not only is this then, in some sense, the natural choice, but it is also a presentation for which we can solve the word problem in a relatively easy, and which is used broadely in such context \jk{by other people? get citations}.

@@

\begin{proof}
\[
    \begin{array}{lcr}
    % https://q.uiver.app/?q=WzAsNixbMiwwLCJcXHRhdV8yXFx0YXVfMVxcdGF1XzJcXHRhdV8xXFx0YXVfMiJdLFswLDEsIlxcdGF1XzFcXHRhdV8yXFx0YXVfMVxcdGF1XzFcXHRhdV8yIl0sWzQsMSwiXFx0YXVfMlxcdGF1XzFcXHRhdV8xXFx0YXVfMlxcdGF1XzEiXSxbMCwyLCJcXHRhdV8xXFx0YXVfMlxcdGF1XzIiXSxbMiwzLCJcXHRhdV8xIl0sWzQsMiwiXFx0YXVfMlxcdGF1XzJcXHRhdV8xIl0sWzAsMSwiYnJhaWQiLDIseyJzdHlsZSI6eyJib2R5Ijp7Im5hbWUiOiJzcXVpZ2dseSJ9fX1dLFswLDIsImJyYWlkIiwwLHsic3R5bGUiOnsiYm9keSI6eyJuYW1lIjoic3F1aWdnbHkifX19XSxbMSwzLCJjYW5jZWwiLDIseyJzdHlsZSI6eyJib2R5Ijp7Im5hbWUiOiJzcXVpZ2dseSJ9fX1dLFszLDQsImNhbmNlbCIsMix7InN0eWxlIjp7ImJvZHkiOnsibmFtZSI6InNxdWlnZ2x5In19fV0sWzIsNSwiY2FuY2VsIiwwLHsic3R5bGUiOnsiYm9keSI6eyJuYW1lIjoic3F1aWdnbHkifX19XSxbNSw0LCJjYW5jZWwiLDAseyJzdHlsZSI6eyJib2R5Ijp7Im5hbWUiOiJzcXVpZ2dseSJ9fX1dXQ==
    \[\begin{tikzcd}
        && {\tau_2\tau_1\tau_2\tau_1\tau_2} \\
        {\tau_1\tau_2\tau_1\tau_1\tau_2} &&&& {\tau_2\tau_1\tau_1\tau_2\tau_1} \\
        {\tau_1\tau_2\tau_2} &&&& {\tau_2\tau_2\tau_1} \\
        && {\tau_1}
        \arrow["braid"', squiggly, from=1-3, to=2-1]
        \arrow["braid", squiggly, from=1-3, to=2-5]
        \arrow["cancel"', squiggly, from=2-1, to=3-1]
        \arrow["cancel"', squiggly, from=3-1, to=4-3]
        \arrow["cancel", squiggly, from=2-5, to=3-5]
        \arrow["cancel", squiggly, from=3-5, to=4-3]
    \end{tikzcd}\]
    &
    \text{and}
    &
    % https://q.uiver.app/?q=WzAsNSxbMiwwLCJcXHRhdV8yXFx0YXVfMVxcdGF1XzJcXHRhdV8yIl0sWzAsMSwiXFx0YXVfMVxcdGF1XzJcXHRhdV8xXFx0YXVfMiJdLFsyLDQsIlxcdGF1XzJcXHRhdV8xIl0sWzAsMiwiXFx0YXVfMVxcdGF1XzJcXHRhdV8xXFx0YXVfMiJdLFsxLDMsIlxcdGF1XzFcXHRhdV8xXFx0YXVfMlxcdGF1XzEiXSxbMCwxLCJicmFpZCIsMix7InN0eWxlIjp7ImJvZHkiOnsibmFtZSI6InNxdWlnZ2x5In19fV0sWzAsMiwiY2FuY2VsIiwwLHsic3R5bGUiOnsiYm9keSI6eyJuYW1lIjoic3F1aWdnbHkifX19XSxbMSwzLCJicmFpZCIsMix7InN0eWxlIjp7ImJvZHkiOnsibmFtZSI6InNxdWlnZ2x5In19fV0sWzMsNCwiYnJhaWQiLDIseyJzdHlsZSI6eyJib2R5Ijp7Im5hbWUiOiJzcXVpZ2dseSJ9fX1dLFs0LDIsImNhbmNlbCIsMix7InN0eWxlIjp7ImJvZHkiOnsibmFtZSI6InNxdWlnZ2x5In19fV1d
    \[\begin{tikzcd}
        && {\tau_2\tau_1\tau_2\tau_2} \\
        {\tau_1\tau_2\tau_1\tau_2} \\
        {\tau_1\tau_2\tau_1\tau_2} \\
        & {\tau_1\tau_1\tau_2\tau_1} \\
        && {\tau_2\tau_1}
        \arrow["braid"', squiggly, from=1-3, to=2-1]
        \arrow["cancel", squiggly, from=1-3, to=5-3]
        \arrow["braid"', squiggly, from=2-1, to=3-1]
        \arrow["braid"', squiggly, from=3-1, to=4-2]
        \arrow["cancel"', squiggly, from=4-2, to=5-3]
    \end{tikzcd}\]
    \end{array}
\]
\end{proof}

>>>>

Connecting it all back to the language $\PiLang$ we are dealing with, it is possible to construct a simlar, yet simplified language $\PiHatLang$ (introduced at \cref{sec:equivalence}), which operates on adjacent transpositions, but still preservers much of $\PiLang$ structure. Thus, for the proof, a presentation based on adjacent transpositions is used, called \emph{Coxeter presentation}. Not only is this then, in some sense, the natural choice, but it is also a presentation for which we can solve the word problem in a relatively easy, and which is used broadely in such context \jk{by other people? get citations}.

@@

\begin{proof}
  \[
    \begin{array}{lr}
    % https://q.uiver.app/?q=WzAsNixbMiwwLCJcXHRhdV8yXFx0YXVfMVxcdGF1XzJcXHRhdV8xXFx0YXVfMiJdLFswLDEsIlxcdGF1XzFcXHRhdV8yXFx0YXVfMVxcdGF1XzFcXHRhdV8yIl0sWzQsMSwiXFx0YXVfMlxcdGF1XzFcXHRhdV8xXFx0YXVfMlxcdGF1XzEiXSxbMCwyLCJcXHRhdV8xXFx0YXVfMlxcdGF1XzIiXSxbMiwzLCJcXHRhdV8xIl0sWzQsMiwiXFx0YXVfMlxcdGF1XzJcXHRhdV8xIl0sWzAsMSwiYnJhaWQiLDIseyJzdHlsZSI6eyJib2R5Ijp7Im5hbWUiOiJzcXVpZ2dseSJ9fX1dLFswLDIsImJyYWlkIiwwLHsic3R5bGUiOnsiYm9keSI6eyJuYW1lIjoic3F1aWdnbHkifX19XSxbMSwzLCJjYW5jZWwiLDIseyJzdHlsZSI6eyJib2R5Ijp7Im5hbWUiOiJzcXVpZ2dseSJ9fX1dLFszLDQsImNhbmNlbCIsMix7InN0eWxlIjp7ImJvZHkiOnsibmFtZSI6InNxdWlnZ2x5In19fV0sWzIsNSwiY2FuY2VsIiwwLHsic3R5bGUiOnsiYm9keSI6eyJuYW1lIjoic3F1aWdnbHkifX19XSxbNSw0LCJjYW5jZWwiLDAseyJzdHlsZSI6eyJib2R5Ijp7Im5hbWUiOiJzcXVpZ2dseSJ9fX1dXQ==
    \begin{tikzcd}
        && {\tau_2\tau_1\tau_2\tau_1\tau_2} \\
        {\tau_1\tau_2\tau_1\tau_1\tau_2} &&&& {\tau_2\tau_1\tau_1\tau_2\tau_1} \\
        {\tau_1\tau_2\tau_2} &&&& {\tau_2\tau_2\tau_1} \\
        && {\tau_1}
        \arrow["braid"', squiggly, from=1-3, to=2-1]
        \arrow["braid", squiggly, from=1-3, to=2-5]
        \arrow["cancel"', squiggly, from=2-1, to=3-1]
        \arrow["cancel"', squiggly, from=3-1, to=4-3]
        \arrow["cancel", squiggly, from=2-5, to=3-5]
        \arrow["cancel", squiggly, from=3-5, to=4-3]
    \end{tikzcd}
    &
    % https://q.uiver.app/?q=WzAsNSxbMiwwLCJcXHRhdV8yXFx0YXVfMVxcdGF1XzJcXHRhdV8yIl0sWzAsMSwiXFx0YXVfMVxcdGF1XzJcXHRhdV8xXFx0YXVfMiJdLFsyLDQsIlxcdGF1XzJcXHRhdV8xIl0sWzAsMiwiXFx0YXVfMVxcdGF1XzJcXHRhdV8xXFx0YXVfMiJdLFsxLDMsIlxcdGF1XzFcXHRhdV8xXFx0YXVfMlxcdGF1XzEiXSxbMCwxLCJicmFpZCIsMix7InN0eWxlIjp7ImJvZHkiOnsibmFtZSI6InNxdWlnZ2x5In19fV0sWzAsMiwiY2FuY2VsIiwwLHsic3R5bGUiOnsiYm9keSI6eyJuYW1lIjoic3F1aWdnbHkifX19XSxbMSwzLCJicmFpZCIsMix7InN0eWxlIjp7ImJvZHkiOnsibmFtZSI6InNxdWlnZ2x5In19fV0sWzMsNCwiYnJhaWQiLDIseyJzdHlsZSI6eyJib2R5Ijp7Im5hbWUiOiJzcXVpZ2dseSJ9fX1dLFs0LDIsImNhbmNlbCIsMix7InN0eWxlIjp7ImJvZHkiOnsibmFtZSI6InNxdWlnZ2x5In19fV1d
    \begin{tikzcd}
        && {\tau_2\tau_1\tau_2\tau_2} \\
        {\tau_1\tau_2\tau_1\tau_2} \\
        {\tau_1\tau_2\tau_1\tau_2} \\
        & {\tau_1\tau_1\tau_2\tau_1} \\
        && {\tau_2\tau_1}
        \arrow["braid"', squiggly, from=1-3, to=2-1]
        \arrow["cancel", squiggly, from=1-3, to=5-3]
        \arrow["braid"', squiggly, from=2-1, to=3-1]
        \arrow["braid"', squiggly, from=3-1, to=4-2]
        \arrow["cancel"', squiggly, from=4-2, to=5-3]
    \end{tikzcd}
    \end{array}
  \]
\end{proof}
